---
title: "Run A"
author: "Heather Welch"
date: "5/22/2018"
output: 
  html_document:
    code_folding: hide
    #toc: true
    #toc_depth: 3
    #toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
##
library(tidyverse)
library(raster)
library(sp)
library(tidyverse)
library(rworldmap)
library(rgdal)
library(rasterVis)
library(RColorBrewer)
library(ggmap)
library(grid)
library(lattice)
library(gridExtra)
library(maptools)
library(dplyr)
library(reshape)
library(pracma)
library(magick)
library(png)
library(maps)
library(purrr)
```
## scenario A--> isolating the effect of swordfish weightings (5 runs, weightings are the same for both algorithms)  
weightings <-c(0,0,0,0,0.1) #run A.1  
weightings <-c(0,0,0,0,0.3) #run A.2  
weightings <-c(0,0,0,0,0.5) #run A.3  
weightings <-c(0,0,0,0,0.7) #run A.4  
weightings <-c(0,0,0,0,0.9) #run A.5  


```{r , echo=FALSE, out.width='25%'}
weightings <-c(0,0,0,0,0.1) #run A.1  
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw.png")
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.png")
image_list=list(a,b,c,d) %>% unlist
knitr::include_graphics(image_list)
weightings <-c(0,0,0,0,0.3) #run A.2
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw.png")
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.png")
image_list=list(a,b,c,d) %>% unlist
knitr::include_graphics(image_list)
weightings <-c(0,0,0,0,0.5) #run A.3  
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw.png")
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.png")
image_list=list(a,b,c,d) %>% unlist
knitr::include_graphics(image_list)
weightings <-c(0,0,0,0,0.7) #run A.4 
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw.png")
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.png")
image_list=list(a,b,c,d) %>% unlist
knitr::include_graphics(image_list)
weightings <-c(0,0,0,0,0.9) #run A.5  
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw.png")
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.png")
image_list=list(a,b,c,d) %>% unlist
knitr::include_graphics(image_list)
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/Model Prediction Plots/daily_predictions/swor/swor_1995-09-11_mean.png")
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/Model Prediction Plots/daily_predictions/lbst_nolat/lbst_nolat_1995-09-11_mean.png")
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/Model Prediction Plots/daily_predictions/blshobs/blshobs_1995-09-11_mean.png")
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/Model Prediction Plots/daily_predictions/blshtrk_nolat/blshtrk_nolat_1995-09-11_mean.png")
image_list=list(a,b,c,d) %>% unlist
knitr::include_graphics(image_list)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
