---
title: "Run C"
author: "Heather Welch"
date: "5/22/2018"
output: 
  html_document:
    code_folding: hide
    #toc: true
    #toc_depth: 3
    #toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
##
library(tidyverse)
library(raster)
library(sp)
library(tidyverse)
library(rworldmap)
library(rgdal)
library(rasterVis)
library(RColorBrewer)
library(ggmap)
library(grid)
library(lattice)
library(gridExtra)
library(maptools)
library(dplyr)
library(reshape)
library(pracma)
library(magick)
library(png)
library(maps)
library(purrr)

thresholds=read.csv("/Users/heatherwelch/Dropbox/EcoEast_EcoROMS_comparison_ms/EcoCast_EcoROMS_comparison_ms/hindcast_ms/summarize/csvs/D_thresholds_weighting_comparison.csv")
path = "/Volumes/EcoCast_SeaGate/ERD_DOM/EcoCast_CodeArchive"
staticdir=paste0(path,"/static_variables/")
studyarea=readOGR(dsn=staticdir,layer="sa_square_coast3")
```
## scenario D--> testing the ability to manage swordfish and leatherback, tailored based on above results (5 runs, weightings are the same for both algorithms)  
# C.3 was the best for Marxan, the Bs were the best for EcoROMS. Seems like its best when lbst is greater than swor  
weightings <-c(0,0,0,-0.5,0.1) #run D.1  
weightings <-c(0,0,0,-0.5,0.3) #run D.2  
weightings <-c(0,0,0,-0.7,0.1) #run D.3  
weightings <-c(0,0,0,-0.7,0.3) #run D.4  
weightings <-c(0,0,0,-0.7,0.5) #run D.5  


```{r , echo=FALSE, out.width='25%'}
weightings <-c(0,0,0,-0.5,0.1) #run D.1 
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw.png")
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.png")
image_list=list(a,b,c,d) %>% unlist
knitr::include_graphics(image_list)
weightings <-c(0,0,0,-0.5,0.3) #run D.2 
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw.png")
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.png")
image_list=list(a,b,c,d) %>% unlist
knitr::include_graphics(image_list)
weightings <-c(0,0,0,-0.7,0.1) #run D.3  
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw.png")
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.png")
image_list=list(a,b,c,d) %>% unlist
knitr::include_graphics(image_list)
weightings <-c(0,0,0,-0.7,0.3) #run D.4
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw.png")
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.png")
image_list=list(a,b,c,d) %>% unlist
knitr::include_graphics(image_list)
weightings <-c(0,0,0,-0.7,0.5) #run D.5 
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.png")
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw.png")
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.png")
image_list=list(a,b,c,d) %>% unlist
knitr::include_graphics(image_list)
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/Model Prediction Plots/daily_predictions/swor/swor_1995-09-11_mean.png")
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/Model Prediction Plots/daily_predictions/lbst_nolat/lbst_nolat_1995-09-11_mean.png")
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/Model Prediction Plots/daily_predictions/blshobs/blshobs_1995-09-11_mean.png")
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/Model Prediction Plots/daily_predictions/blshtrk_nolat/blshtrk_nolat_1995-09-11_mean.png")
image_list=list(a,b,c,d) %>% unlist
knitr::include_graphics(image_list)
```

### visualization of threshold effect at 10% allowable leatherback bycatch risk. Red = waters below threshold (do not fish), blue = waters above threshold (fist), white = waters at threshold (NA, values not considered fishable or unfishable)

```{r , echo=FALSE, out.width='25%'}
cuts=c(-1,0,1)
pal=colorRampPalette(c("red","blue"))
thresh10=thresholds %>% filter(catch==0.1)

i=1
weightings <-c(0,0,0,-0.5,0.1) #run D.1  
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() %>% crop(.,extent(studyarea))
a[a>thresh10$EcoROMS_original[i]]<-1
a[a<thresh10$EcoROMS_original[i]]<--1
a[a==thresh10$EcoROMS_original[i]]<-NA
plot(a,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original[i],3)))
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() 
b[b>thresh10$EcoROMS_original_unscaled[i]]<-1
b[b<thresh10$EcoROMS_original_unscaled[i]]<--1
b[b==thresh10$EcoROMS_original_unscaled[i]]<-NA
plot(b,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original_unscaled[i],3)))
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_nocost_",paste0(weightings,collapse="_"),"_1995-09-11_raw.grd") %>% raster() 
c[c>thresh10$Marxan_raw[i]]<-1
c[c<thresh10$Marxan_raw[i]]<--1
c[c==thresh10$Marxan_raw[i]]<-NA
plot(c,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw[i],3)))
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.grd") %>% raster() 
d[d>thresh10$Marxan_raw_unscaled[i]]<-1
d[d<thresh10$Marxan_raw_unscaled[i]]<--1
d[d==thresh10$Marxan_raw_unscaled[i]]<-NA
plot(d,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw_unscaled[i],3)))

i=2
weightings <-c(0,0,0,-0.5,0.3) #run D.2  
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() %>% crop(.,extent(studyarea))
a[a>thresh10$EcoROMS_original[i]]<-1
a[a<thresh10$EcoROMS_original[i]]<--1
a[a==thresh10$EcoROMS_original[i]]<-NA
plot(a,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original[i],3)))
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() 
b[b>thresh10$EcoROMS_original_unscaled[i]]<-1
b[b<thresh10$EcoROMS_original_unscaled[i]]<--1
b[b==thresh10$EcoROMS_original_unscaled[i]]<-NA
plot(b,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original_unscaled[i],3)))
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_nocost_",paste0(weightings,collapse="_"),"_1995-09-11_raw.grd") %>% raster() 
c[c>thresh10$Marxan_raw[i]]<-1
c[c<thresh10$Marxan_raw[i]]<--1
c[c==thresh10$Marxan_raw[i]]<-NA
plot(c,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw[i],3)))
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.grd") %>% raster() 
d[d>thresh10$Marxan_raw_unscaled[i]]<-1
d[d<thresh10$Marxan_raw_unscaled[i]]<--1
d[d==thresh10$Marxan_raw_unscaled[i]]<-NA
plot(d,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw_unscaled[i],3)))

i=3
weightings <-c(0,0,0,-0.7,0.1) #run D.3 
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() %>% crop(.,extent(studyarea))
a[a>thresh10$EcoROMS_original[i]]<-1
a[a<thresh10$EcoROMS_original[i]]<--1
a[a==thresh10$EcoROMS_original[i]]<-NA
plot(a,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original[i],3)))
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() 
b[b>thresh10$EcoROMS_original_unscaled[i]]<-1
b[b<thresh10$EcoROMS_original_unscaled[i]]<--1
b[b==thresh10$EcoROMS_original_unscaled[i]]<-NA
plot(b,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original_unscaled[i],3)))
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_nocost_",paste0(weightings,collapse="_"),"_1995-09-11_raw.grd") %>% raster() 
c[c>thresh10$Marxan_raw[i]]<-1
c[c<thresh10$Marxan_raw[i]]<--1
c[c==thresh10$Marxan_raw[i]]<-NA
plot(c,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw[i],3)))
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.grd") %>% raster() 
d[d>thresh10$Marxan_raw_unscaled[i]]<-1
d[d<thresh10$Marxan_raw_unscaled[i]]<--1
d[d==thresh10$Marxan_raw_unscaled[i]]<-NA
plot(d,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw_unscaled[i],3)))

i=4
weightings <-c(0,0,0,-0.7,0.3) #run D.4 
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() %>% crop(.,extent(studyarea))
a[a>thresh10$EcoROMS_original[i]]<-1
a[a<thresh10$EcoROMS_original[i]]<--1
a[a==thresh10$EcoROMS_original[i]]<-NA
plot(a,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original[i],3)))
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() 
b[b>thresh10$EcoROMS_original_unscaled[i]]<-1
b[b<thresh10$EcoROMS_original_unscaled[i]]<--1
b[b==thresh10$EcoROMS_original_unscaled[i]]<-NA
plot(b,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original_unscaled[i],3)))
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_nocost_",paste0(weightings,collapse="_"),"_1995-09-11_raw.grd") %>% raster() 
c[c>thresh10$Marxan_raw[i]]<-1
c[c<thresh10$Marxan_raw[i]]<--1
c[c==thresh10$Marxan_raw[i]]<-NA
plot(c,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw[i],3)))
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.grd") %>% raster() 
d[d>thresh10$Marxan_raw_unscaled[i]]<-1
d[d<thresh10$Marxan_raw_unscaled[i]]<--1
d[d==thresh10$Marxan_raw_unscaled[i]]<-NA
plot(d,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw_unscaled[i],3)))

i=5
weightings <-c(0,0,0,-0.7,0.5) #run D.5  
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() %>% crop(.,extent(studyarea))
a[a>thresh10$EcoROMS_original[i]]<-1
a[a<thresh10$EcoROMS_original[i]]<--1
a[a==thresh10$EcoROMS_original[i]]<-NA
plot(a,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original[i],3)))
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() 
b[b>thresh10$EcoROMS_original_unscaled[i]]<-1
b[b<thresh10$EcoROMS_original_unscaled[i]]<--1
b[b==thresh10$EcoROMS_original_unscaled[i]]<-NA
plot(b,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original_unscaled[i],3)))
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_nocost_",paste0(weightings,collapse="_"),"_1995-09-11_raw.grd") %>% raster() 
c[c>thresh10$Marxan_raw[i]]<-1
c[c<thresh10$Marxan_raw[i]]<--1
c[c==thresh10$Marxan_raw[i]]<-NA
plot(c,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw[i],3)))
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.grd") %>% raster() 
d[d>thresh10$Marxan_raw_unscaled[i]]<-1
d[d<thresh10$Marxan_raw_unscaled[i]]<--1
d[d==thresh10$Marxan_raw_unscaled[i]]<-NA
plot(d,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw_unscaled[i],3)))

```

### visualization of threshold effect at 50% allowable leatherback bycatch risk. Red = waters below threshold (do not fish), blue = waters above threshold (fist), white = waters at threshold (NA, values not considered fishable or unfishable)

```{r , echo=FALSE, out.width='25%'}
cuts=c(-1,0,1)
pal=colorRampPalette(c("red","blue"))
thresh10=thresholds %>% filter(catch==0.5)

i=1
weightings <-c(0,0,0,-0.5,0.1) #run D.1
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() %>% crop(.,extent(studyarea))
a[a>thresh10$EcoROMS_original[i]]<-1
a[a<thresh10$EcoROMS_original[i]]<--1
a[a==thresh10$EcoROMS_original[i]]<-NA
plot(a,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original[i],3)))
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() 
b[b>thresh10$EcoROMS_original_unscaled[i]]<-1
b[b<thresh10$EcoROMS_original_unscaled[i]]<--1
b[b==thresh10$EcoROMS_original_unscaled[i]]<-NA
plot(b,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original_unscaled[i],3)))
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_nocost_",paste0(weightings,collapse="_"),"_1995-09-11_raw.grd") %>% raster() 
c[c>thresh10$Marxan_raw[i]]<-1
c[c<thresh10$Marxan_raw[i]]<--1
c[c==thresh10$Marxan_raw[i]]<-NA
plot(c,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw[i],3)))
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.grd") %>% raster() 
d[d>thresh10$Marxan_raw_unscaled[i]]<-1
d[d<thresh10$Marxan_raw_unscaled[i]]<--1
d[d==thresh10$Marxan_raw_unscaled[i]]<-NA
plot(d,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw_unscaled[i],3)))

i=2
weightings <-c(0,0,0,-0.5,0.3) #run D.2  
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() %>% crop(.,extent(studyarea))
a[a>thresh10$EcoROMS_original[i]]<-1
a[a<thresh10$EcoROMS_original[i]]<--1
a[a==thresh10$EcoROMS_original[i]]<-NA
plot(a,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original[i],3)))
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() 
b[b>thresh10$EcoROMS_original_unscaled[i]]<-1
b[b<thresh10$EcoROMS_original_unscaled[i]]<--1
b[b==thresh10$EcoROMS_original_unscaled[i]]<-NA
plot(b,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original_unscaled[i],3)))
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_nocost_",paste0(weightings,collapse="_"),"_1995-09-11_raw.grd") %>% raster() 
c[c>thresh10$Marxan_raw[i]]<-1
c[c<thresh10$Marxan_raw[i]]<--1
c[c==thresh10$Marxan_raw[i]]<-NA
plot(c,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw[i],3)))
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.grd") %>% raster() 
d[d>thresh10$Marxan_raw_unscaled[i]]<-1
d[d<thresh10$Marxan_raw_unscaled[i]]<--1
d[d==thresh10$Marxan_raw_unscaled[i]]<-NA
plot(d,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw_unscaled[i],3)))

i=3
weightings <-c(0,0,0,-0.7,0.1) #run D.3  
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() %>% crop(.,extent(studyarea))
a[a>thresh10$EcoROMS_original[i]]<-1
a[a<thresh10$EcoROMS_original[i]]<--1
a[a==thresh10$EcoROMS_original[i]]<-NA
plot(a,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original[i],3)))
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() 
b[b>thresh10$EcoROMS_original_unscaled[i]]<-1
b[b<thresh10$EcoROMS_original_unscaled[i]]<--1
b[b==thresh10$EcoROMS_original_unscaled[i]]<-NA
plot(b,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original_unscaled[i],3)))
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_nocost_",paste0(weightings,collapse="_"),"_1995-09-11_raw.grd") %>% raster() 
c[c>thresh10$Marxan_raw[i]]<-1
c[c<thresh10$Marxan_raw[i]]<--1
c[c==thresh10$Marxan_raw[i]]<-NA
plot(c,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw[i],3)))
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.grd") %>% raster() 
d[d>thresh10$Marxan_raw_unscaled[i]]<-1
d[d<thresh10$Marxan_raw_unscaled[i]]<--1
d[d==thresh10$Marxan_raw_unscaled[i]]<-NA
plot(d,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw_unscaled[i],3)))

i=4
weightings <-c(0,0,0,-0.7,0.3) #run D.4 
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() %>% crop(.,extent(studyarea))
a[a>thresh10$EcoROMS_original[i]]<-1
a[a<thresh10$EcoROMS_original[i]]<--1
a[a==thresh10$EcoROMS_original[i]]<-NA
plot(a,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original[i],3)))
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() 
b[b>thresh10$EcoROMS_original_unscaled[i]]<-1
b[b<thresh10$EcoROMS_original_unscaled[i]]<--1
b[b==thresh10$EcoROMS_original_unscaled[i]]<-NA
plot(b,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original_unscaled[i],3)))
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_nocost_",paste0(weightings,collapse="_"),"_1995-09-11_raw.grd") %>% raster() 
c[c>thresh10$Marxan_raw[i]]<-1
c[c<thresh10$Marxan_raw[i]]<--1
c[c==thresh10$Marxan_raw[i]]<-NA
plot(c,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw[i],3)))
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.grd") %>% raster() 
d[d>thresh10$Marxan_raw_unscaled[i]]<-1
d[d<thresh10$Marxan_raw_unscaled[i]]<--1
d[d==thresh10$Marxan_raw_unscaled[i]]<-NA
plot(d,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw_unscaled[i],3)))

i=5
weightings <-c(0,0,0,-0.7,0.5) #run D.5  
a=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() %>% crop(.,extent(studyarea))
a[a>thresh10$EcoROMS_original[i]]<-1
a[a<thresh10$EcoROMS_original[i]]<--1
a[a==thresh10$EcoROMS_original[i]]<-NA
plot(a,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original[i],3)))
b=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/mean/EcoROMS_original_unscaled_",paste0(weightings,collapse="_"),"_1995-09-11_mean.grd") %>% raster() 
b[b>thresh10$EcoROMS_original_unscaled[i]]<-1
b[b<thresh10$EcoROMS_original_unscaled[i]]<--1
b[b==thresh10$EcoROMS_original_unscaled[i]]<-NA
plot(b,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$EcoROMS_original_unscaled[i],3)))
c=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_nocost_",paste0(weightings,collapse="_"),"_1995-09-11_raw.grd") %>% raster() 
c[c>thresh10$Marxan_raw[i]]<-1
c[c<thresh10$Marxan_raw[i]]<--1
c[c==thresh10$Marxan_raw[i]]<-NA
plot(c,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw[i],3)))
d=paste0("/Users/heatherwelch/Dropbox/Eco-ROMS/EcoROMSruns/output/hindcast_ms/marxan/marxan_",paste0(weightings,collapse="_"),"_1995-09-11_raw_unscaled.grd") %>% raster() 
d[d>thresh10$Marxan_raw_unscaled[i]]<-1
d[d<thresh10$Marxan_raw_unscaled[i]]<--1
d[d==thresh10$Marxan_raw_unscaled[i]]<-NA
plot(d,breaks=cuts,col=pal(2),legend=F,axes=F,box=F,main=paste0("weighting= ",thresh10$weighting[i],", threshold= ",round(thresh10$Marxan_raw_unscaled[i],3)))

```