---
title: "WeightingsXAlgorithm Poltly"
author: "Heather Welch"
date: "6/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(RColorBrewer)
```

## Weightings scenarios

namesrisk<-c("Blue shark bycatch","Blue sharks","Sea lions","Leatherbacks","Swordfish")

**scenario A--> isolating the effect of swordfish weightings (5 runs, weightings are the same for both algorithms)**  
weightings <-c(0,0,0,0,0.1) #run A.1  
weightings <-c(0,0,0,0,0.3) #run A.2  
weightings <-c(0,0,0,0,0.5) #run A.3  
weightings <-c(0,0,0,0,0.7) #run A.4  
weightings <-c(0,0,0,0,0.9) #run A.5  

**scenario B--> isolating the effect of leatherback weightings (5 runs, weightings are the same for both algorithms)**  
weightings <-c(0,0,0,-0.1,0) #run B.1  
weightings <-c(0,0,0,-0.3,0) #run B.2  
weightings <-c(0,0,0,-0.5,0) #run B.3  
weightings <-c(0,0,0,-0.7,0) #run B.4  
weightings <-c(0,0,0,-0.9,0) #run B.5  

**scenario C--> testing the ability to manage swordfish and leatherback equally (5 runs, weightings are the same for both algorithms)**  
weightings <-c(0,0,0,-0.1,0.1) #run C.1  
weightings <-c(0,0,0,-0.3,0.3) #run C.2  
weightings <-c(0,0,0,-0.5,0.5) #run C.3  
weightings <-c(0,0,0,-0.7,0.7) #run C.4  
weightings <-c(0,0,0,-0.9,0.9) #run C.5  

**scenario D--> testing the ability to manage swordfish and leatherback, tailored based on above results (5 runs, weightings are the same for both algorithms)**  
C.3 was the best for Marxan, the Bs were the best for EcoROMS. Seems like its best when lbst is greater than swor  
weightings <-c(0,0,0,-0.5,0.1) #run D.1  
weightings <-c(0,0,0,-0.5,0.3) #run D.2  
weightings <-c(0,0,0,-0.7,0.1) #run D.3  
weightings <-c(0,0,0,-0.7,0.3) #run D.4  
weightings <-c(0,0,0,-0.7,0.5) #run D.5  

```{r,echo=FALSE}
csvdir="hindcast_ms/summarize/csvs/"
plotdir="hindcast_ms/summarize/plots/"
run="A-D"

file_list=list.files("/Users/heatherwelch/Dropbox/EcoEast_EcoROMS_comparison_ms/EcoCast_EcoROMS_comparison_ms/hindcast_ms/summarize/csvs") %>% grep("availcatch_algorithm",.,value=T)
master=list()
for (file in file_list){
  a=read.csv(paste0("/Users/heatherwelch/Dropbox/EcoEast_EcoROMS_comparison_ms/EcoCast_EcoROMS_comparison_ms/hindcast_ms/summarize/csvs/",file))
  name=gsub("_availcatch_algorithm_comparison.csv","",file)
  a$run=name
  assign(name,a)
  master[[name]]<-a
}

fullon=do.call("rbind",master)
df=fullon %>% dplyr::filter(limit_target=="swordfish")
df$product=gsub("EcorROMS","EcoROMS",df$product)

colorCount=length(unique(df$run))
getPalette = colorRampPalette(brewer.pal(11, "Spectral"))
mycolors=c(brewer.pal("Greens",n=5),brewer.pal("Blues",n=5),brewer.pal("Reds",n=5),brewer.pal("Purples",n=5))

a=ggplot(df,aes(x=swor,y=lbst,group=run,color=run))+geom_line()+geom_point(size=.5) +facet_wrap(~product,nrow=1)
a=a+ggtitle(label = "Trade-offs between swordfish availability and leatherback bycatch for each algorithm and run")+labs(x=paste0("% of swordfish available to catch"))+labs(y="% of leathbacks bycaught")
a=a+theme(panel.background = element_rect(fill=NA,color="black"),strip.background =element_rect(fill=NA))+ theme(axis.line = element_line(colour = "black"))+ theme(text = element_text(size=8),axis.text = element_text(size=8),plot.title = element_text(hjust = 0,size = 9))
a=a+scale_color_manual(values=mycolors)
a=a+theme(legend.title = element_text(size=5),legend.position=c(.13,.9),legend.justification = c(.9,.9))+theme(legend.background = element_blank())+theme(legend.text=element_text(size=8),legend.box.background = element_rect(colour = "black"))+theme(legend.key=element_blank())+theme(legend.key.size = unit(.9,'lines'))
b=a
#a=ggplotly(a)

df2=fullon %>% filter(limit_target=="leatherback")
df2$product=gsub("EcorROMS","EcoROMS",df$product)

a=ggplot(df2,aes(x=lbst,y=swor,group=run,color=run))+geom_line()+geom_point(size=.5) +facet_wrap(~product,nrow=1)
a=a+ggtitle(label = "Trade-offs between leatherback bycatch and swordfish availability for each algorithm and run")+labs(x=paste0("% of leathbacks bycaught"))+labs(y="% of swordfish available to catch")
a=a+theme(panel.background = element_rect(fill=NA,color="black"),strip.background =element_rect(fill=NA))+ theme(axis.line = element_line(colour = "black"))+ theme(text = element_text(size=8),axis.text = element_text(size=8),plot.title = element_text(hjust = 0,size = 9))
a=a+scale_color_manual(values=mycolors)
a=a+theme(legend.title = element_text(size=5),legend.position=c(.9,.4),legend.justification = c(.9,.9))+theme(legend.background = element_blank())+theme(legend.text=element_text(size=8),legend.box.background = element_rect(colour = "black"))+theme(legend.key=element_blank())+theme(legend.key.size = unit(.9,'lines'))

ggplotly(b,session="knitr")
ggplotly(a,session="knitr")

```
